---
title: "An Incremental `ggplot` Tutorial"
subtitle: "Use <span style='font-size:50px'>&#8678;</span> and <span style='font-size:50px'>&#8680;</span> to navigate."
author: "Andy Grogan-Kaylor"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu, animate.css]
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{css, echo=FALSE}

@import url('https://fonts.googleapis.com/css2?family=Montserrat&display=swap');
.title-slide { 
  color: #ffcb05;
  background-color: #00274C; 
}
.title-slide h1 {
    color: #ffcb05;
}
pre {
  white-space: pre-wrap;
}
h1, h2, h3 {
  font-family: 'Montserrat', sans-serif;
}
body { 
    font-family: 'Montserrat', sans-serif;
}
.author, .date {
  font-family: 'Montserrat', sans-serif;
}

```

```{r setup, include = F}

# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scracth can be time consuming

knitr::opts_chunk$set(fig.width = 6, 
                      message = FALSE, 
                      warning = FALSE, 
                      comment = "", 
                      cache = FALSE, 
                      fig.retina = 3)

library(flipbookr)

library(tidyverse)

library(xaringanExtra)

xaringanExtra::use_tile_view()

# xaringanExtra::use_slide_tone()

xaringanExtra::use_share_again()


```

# How To Navigate This Presentation

* Use the <span style="font-size:100px">&#8678;</span> and <span style="font-size:100px">&#8680;</span> keys to move through the presentation.
* Press *o* for *panel overview*.

---
class: animated, slideInRight
# Introduction

This is an *incremental* demonstration of building a more sophisticated plot of the global families data.


---
class: animated, slideInRight
# Load The Data

```{r}

library(ggplot2) # call the library

load("MICSsimulated.RData") # load the data

```

---
class: animated, slideInRight
# Change Variables To Categorical

```{r}

MICSsimulated$aggression <- 
  factor(MICSsimulated$aggression, # original numeric variable
         levels = c(0, 1), 
         labels = c("no aggression", "aggression"), 
         ordered = TRUE) # whether order matters

```

```{r}

MICSsimulated$cd1 <- 
  factor(MICSsimulated$cd1, # original numeric variable
         levels = c(0, 1), 
         labels = c("no spank", "spank"), 
         ordered = TRUE) # whether order matters

```

---
class: animated, slideInRight
# Bar Graph With Color Fill

We build up the plot step by step. 

```{r graph1, include = FALSE, fig.height=4}

ggplot(MICSsimulated,
       aes(
         x = cd1, #BREAK2
         fill = aggression #BREAK4
         )) +
  geom_bar( #BREAK3
    position = position_dodge() #BREAK5
  ) + #BREAK3
  labs( 
    title = "Spanking and Aggression", #BREAK6
    x = "spanking", #BREAK7
    y = "count" #BREAK8
    ) + 
  scale_fill_manual( #BREAK9
    values = c("#1CABE2", "#D8D1C9") #BREAK9
    ) + #BREAK9
  theme_minimal() + #BREAK9
  theme(
    title = element_text(size = rel(1.5)), #BREAK9
    axis.text = element_text(size = rel(1.5)) #BREAK9
    ) 

```

---

```{r, code = knitr::knit_code$get("graph1"), eval = FALSE, echo = FALSE}
```

`r chunk_reveal("graph1", break_type = "non_seq", widths = c(3,2))`





